openTSNE: a modular Python library for t-SNE dimensionality reduction and embedding

### 2021-03-17 paper/policar2020-opentsne.tex
Embed bibliography into tex file

\bibliographystyle{bmc-mathphys} % Style BST file (bmc-mathphys, vancouver, spbasic).
\bibliography{references}      % Bibliography file (usually '*.bib' )

>>>>

%% Bibliography
\begin{thebibliography}{28}
% BibTex style file: bmc-mathphys.bst (version 2.1), 2014-07-24
\ifx \bisbn   \undefined \def \bisbn  #1{ISBN #1}\fi
\ifx \binits  \undefined \def \binits#1{#1}\fi
\ifx \bauthor  \undefined \def \bauthor#1{#1}\fi
\ifx \batitle  \undefined \def \batitle#1{#1}\fi
\ifx \bjtitle  \undefined \def \bjtitle#1{#1}\fi
\ifx \bvolume  \undefined \def \bvolume#1{\textbf{#1}}\fi
\ifx \byear  \undefined \def \byear#1{#1}\fi
\ifx \bissue  \undefined \def \bissue#1{#1}\fi
\ifx \bfpage  \undefined \def \bfpage#1{#1}\fi
\ifx \blpage  \undefined \def \blpage #1{#1}\fi
\ifx \burl  \undefined \def \burl#1{\textsf{#1}}\fi
\ifx \doiurl  \undefined \def \doiurl#1{\textsf{#1}}\fi
\ifx \betal  \undefined \def \betal{\textit{et al.}}\fi
\ifx \binstitute  \undefined \def \binstitute#1{#1}\fi
\ifx \binstitutionaled  \undefined \def \binstitutionaled#1{#1}\fi
\ifx \bctitle  \undefined \def \bctitle#1{#1}\fi
\ifx \beditor  \undefined \def \beditor#1{#1}\fi
\ifx \bpublisher  \undefined \def \bpublisher#1{#1}\fi
\ifx \bbtitle  \undefined \def \bbtitle#1{#1}\fi
\ifx \bedition  \undefined \def \bedition#1{#1}\fi
\ifx \bseriesno  \undefined \def \bseriesno#1{#1}\fi
\ifx \blocation  \undefined \def \blocation#1{#1}\fi
\ifx \bsertitle  \undefined \def \bsertitle#1{#1}\fi
\ifx \bsnm \undefined \def \bsnm#1{#1}\fi
\ifx \bsuffix \undefined \def \bsuffix#1{#1}\fi
\ifx \bparticle \undefined \def \bparticle#1{#1}\fi
\ifx \barticle \undefined \def \barticle#1{#1}\fi
\ifx \bconfdate \undefined \def \bconfdate #1{#1}\fi
\ifx \botherref \undefined \def \botherref #1{#1}\fi
\ifx \url \undefined \def \url#1{\textsf{#1}}\fi
\ifx \bchapter \undefined \def \bchapter#1{#1}\fi
\ifx \bbook \undefined \def \bbook#1{#1}\fi
\ifx \bcomment \undefined \def \bcomment#1{#1}\fi
\ifx \oauthor \undefined \def \oauthor#1{#1}\fi
\ifx \citeauthoryear \undefined \def \citeauthoryear#1{#1}\fi
\ifx \endbibitem  \undefined \def \endbibitem {}\fi
\ifx \bconflocation  \undefined \def \bconflocation#1{#1}\fi
\ifx \arxivurl  \undefined \def \arxivurl#1{\textsf{#1}}\fi
\csname PreBibitemsHook\endcsname

%%% 1
\bibitem{maaten2008visualizing}
\begin{barticle}
\bauthor{\bsnm{Van Der~Maaten}, \binits{L.}},
\bauthor{\bsnm{Hinton}, \binits{G.}}:
\batitle{{Visualizing data using t-SNE}}.
\bjtitle{Journal of Machine Learning Research}
\bvolume{9}(\bissue{Nov}),
\bfpage{2579}--\blpage{2605}
(\byear{2008})
\end{barticle}
\endbibitem

%%% 2
\bibitem{2018arXivUMAP}
\begin{botherref}
\oauthor{\bsnm{{McInnes}}, \binits{L.}},
\oauthor{\bsnm{{Healy}}, \binits{J.}},
\oauthor{\bsnm{{Melville}}, \binits{J.}}:
{UMAP: Uniform Manifold Approximation and Projection for Dimension Reduction}.
ArXiv e-prints
(2018).
\arxivurl{1802.03426}
\end{botherref}
\endbibitem

%%% 3
\bibitem{macosko2015highly}
\begin{barticle}
\bauthor{\bsnm{Macosko}, \binits{E.Z.}},
\bauthor{\bsnm{Basu}, \binits{A.}},
\bauthor{\bsnm{Satija}, \binits{R.}},
\bauthor{\bsnm{Nemesh}, \binits{J.}},
\bauthor{\bsnm{Shekhar}, \binits{K.}},
\bauthor{\bsnm{Goldman}, \binits{M.}},
\bauthor{\bsnm{Tirosh}, \binits{I.}},
\bauthor{\bsnm{Bialas}, \binits{A.R.}},
\bauthor{\bsnm{Kamitaki}, \binits{N.}},
\bauthor{\bsnm{Martersteck}, \binits{E.M.}}, \betal:
\batitle{Highly parallel genome-wide expression profiling of individual cells
  using nanoliter droplets}.
\bjtitle{Cell}
\bvolume{161}(\bissue{5}),
\bfpage{1202}--\blpage{1214}
(\byear{2015})
\end{barticle}
\endbibitem

%%% 4
\bibitem{cao2019single}
\begin{barticle}
\bauthor{\bsnm{Cao}, \binits{J.}},
\bauthor{\bsnm{Spielmann}, \binits{M.}},
\bauthor{\bsnm{Qiu}, \binits{X.}},
\bauthor{\bsnm{Huang}, \binits{X.}},
\bauthor{\bsnm{Ibrahim}, \binits{D.M.}},
\bauthor{\bsnm{Hill}, \binits{A.J.}},
\bauthor{\bsnm{Zhang}, \binits{F.}},
\bauthor{\bsnm{Mundlos}, \binits{S.}},
\bauthor{\bsnm{Christiansen}, \binits{L.}},
\bauthor{\bsnm{Steemers}, \binits{F.J.}}, \betal:
\batitle{The single-cell transcriptional landscape of mammalian organogenesis}.
\bjtitle{Nature}
\bvolume{566}(\bissue{7745}),
\bfpage{496}--\blpage{502}
(\byear{2019})
\end{barticle}
\endbibitem

%%% 5
\bibitem{tasic2018shared}
\begin{barticle}
\bauthor{\bsnm{Tasic}, \binits{B.}},
\bauthor{\bsnm{Yao}, \binits{Z.}},
\bauthor{\bsnm{Graybuck}, \binits{L.T.}},
\bauthor{\bsnm{Smith}, \binits{K.A.}},
\bauthor{\bsnm{Nguyen}, \binits{T.N.}},
\bauthor{\bsnm{Bertagnolli}, \binits{D.}},
\bauthor{\bsnm{Goldy}, \binits{J.}},
\bauthor{\bsnm{Garren}, \binits{E.}},
\bauthor{\bsnm{Economo}, \binits{M.N.}},
\bauthor{\bsnm{Viswanathan}, \binits{S.}}, \betal:
\batitle{Shared and distinct transcriptomic cell types across neocortical
  areas}.
\bjtitle{Nature}
\bvolume{563}(\bissue{7729}),
\bfpage{72}--\blpage{78}
(\byear{2018})
\end{barticle}
\endbibitem

%%% 6
\bibitem{hirata2019genetic}
\begin{barticle}
\bauthor{\bsnm{Hirata}, \binits{J.}},
\bauthor{\bsnm{Hosomichi}, \binits{K.}},
\bauthor{\bsnm{Sakaue}, \binits{S.}},
\bauthor{\bsnm{Kanai}, \binits{M.}},
\bauthor{\bsnm{Nakaoka}, \binits{H.}},
\bauthor{\bsnm{Ishigaki}, \binits{K.}},
\bauthor{\bsnm{Suzuki}, \binits{K.}},
\bauthor{\bsnm{Akiyama}, \binits{M.}},
\bauthor{\bsnm{Kishikawa}, \binits{T.}},
\bauthor{\bsnm{Ogawa}, \binits{K.}}, \betal:
\batitle{{Genetic and phenotypic landscape of the major histocompatibilty
  complex region in the Japanese population}}.
\bjtitle{Nature Genetics}
\bvolume{51}(\bissue{3}),
\bfpage{470}--\blpage{480}
(\byear{2019})
\end{barticle}
\endbibitem

%%% 7
\bibitem{beaulaurier2018metagenomic}
\begin{barticle}
\bauthor{\bsnm{Beaulaurier}, \binits{J.}},
\bauthor{\bsnm{Zhu}, \binits{S.}},
\bauthor{\bsnm{Deikus}, \binits{G.}},
\bauthor{\bsnm{Mogno}, \binits{I.}},
\bauthor{\bsnm{Zhang}, \binits{X.-S.}},
\bauthor{\bsnm{Davis-Richardson}, \binits{A.}},
\bauthor{\bsnm{Canepa}, \binits{R.}},
\bauthor{\bsnm{Triplett}, \binits{E.W.}},
\bauthor{\bsnm{Faith}, \binits{J.J.}},
\bauthor{\bsnm{Sebra}, \binits{R.}}, \betal:
\batitle{{Metagenomic binning and association of plasmids with bacterial host
  genomes using DNA methylation}}.
\bjtitle{Nature Biotechnology}
\bvolume{36}(\bissue{1}),
\bfpage{61}
(\byear{2018})
\end{barticle}
\endbibitem

%%% 8
\bibitem{sheth2019spatial}
\begin{barticle}
\bauthor{\bsnm{Sheth}, \binits{R.U.}},
\bauthor{\bsnm{Li}, \binits{M.}},
\bauthor{\bsnm{Jiang}, \binits{W.}},
\bauthor{\bsnm{Sims}, \binits{P.A.}},
\bauthor{\bsnm{Leong}, \binits{K.W.}},
\bauthor{\bsnm{Wang}, \binits{H.H.}}:
\batitle{Spatial metagenomic characterization of microbial biogeography in the
  gut}.
\bjtitle{Nature Biotechnology}
\bvolume{37}(\bissue{8}),
\bfpage{877}--\blpage{883}
(\byear{2019})
\end{barticle}
\endbibitem

%%% 9
\bibitem{tkachev2019differences}
\begin{barticle}
\bauthor{\bsnm{Tkachev}, \binits{A.}},
\bauthor{\bsnm{Stepanova}, \binits{V.}},
\bauthor{\bsnm{Zhang}, \binits{L.}},
\bauthor{\bsnm{Khrameeva}, \binits{E.}},
\bauthor{\bsnm{Zubkov}, \binits{D.}},
\bauthor{\bsnm{Giavalisco}, \binits{P.}},
\bauthor{\bsnm{Khaitovich}, \binits{P.}}:
\batitle{Differences in lipidome and metabolome organization of prefrontal
  cortex among human populations}.
\bjtitle{Scientific Reports}
\bvolume{9}(\bissue{1}),
\bfpage{1}--\blpage{10}
(\byear{2019})
\end{barticle}
\endbibitem

%%% 10
\bibitem{shekhar2016comprehensive}
\begin{barticle}
\bauthor{\bsnm{Shekhar}, \binits{K.}},
\bauthor{\bsnm{Lapan}, \binits{S.W.}},
\bauthor{\bsnm{Whitney}, \binits{I.E.}},
\bauthor{\bsnm{Tran}, \binits{N.M.}},
\bauthor{\bsnm{Macosko}, \binits{E.Z.}},
\bauthor{\bsnm{Kowalczyk}, \binits{M.}},
\bauthor{\bsnm{Adiconis}, \binits{X.}},
\bauthor{\bsnm{Levin}, \binits{J.Z.}},
\bauthor{\bsnm{Nemesh}, \binits{J.}},
\bauthor{\bsnm{Goldman}, \binits{M.}}, \betal:
\batitle{Comprehensive classification of retinal bipolar neurons by single-cell
  transcriptomics}.
\bjtitle{Cell}
\bvolume{166}(\bissue{5}),
\bfpage{1308}--\blpage{1323}
(\byear{2016})
\end{barticle}
\endbibitem

%%% 11
\bibitem{ding2018interpretable}
\begin{barticle}
\bauthor{\bsnm{Ding}, \binits{J.}},
\bauthor{\bsnm{Condon}, \binits{A.}},
\bauthor{\bsnm{Shah}, \binits{S.P.}}:
\batitle{Interpretable dimensionality reduction of single cell transcriptome
  data with deep generative models}.
\bjtitle{Nature Communications}
\bvolume{9}(\bissue{1}),
\bfpage{2002}
(\byear{2018})
\end{barticle}
\endbibitem

%%% 12
\bibitem{becht2019dimensionality}
\begin{barticle}
\bauthor{\bsnm{Becht}, \binits{E.}},
\bauthor{\bsnm{McInnes}, \binits{L.}},
\bauthor{\bsnm{Healy}, \binits{J.}},
\bauthor{\bsnm{Dutertre}, \binits{C.-A.}},
\bauthor{\bsnm{Kwok}, \binits{I.W.}},
\bauthor{\bsnm{Ng}, \binits{L.G.}},
\bauthor{\bsnm{Ginhoux}, \binits{F.}},
\bauthor{\bsnm{Newell}, \binits{E.W.}}:
\batitle{{Dimensionality reduction for visualizing single-cell data using
  UMAP}}.
\bjtitle{Nature Biotechnology}
\bvolume{37}(\bissue{1}),
\bfpage{38}
(\byear{2019})
\end{barticle}
\endbibitem

%%% 13
\bibitem{linderman2019fast}
\begin{barticle}
\bauthor{\bsnm{Linderman}, \binits{G.C.}},
\bauthor{\bsnm{Rachh}, \binits{M.}},
\bauthor{\bsnm{Hoskins}, \binits{J.G.}},
\bauthor{\bsnm{Steinerberger}, \binits{S.}},
\bauthor{\bsnm{Kluger}, \binits{Y.}}:
\batitle{{Fast interpolation-based t-SNE for improved visualization of
  single-cell RNA-seq data}}.
\bjtitle{Nature Methods}
\bvolume{16}(\bissue{3}),
\bfpage{243}--\blpage{245}
(\byear{2019})
\end{barticle}
\endbibitem

%%% 14
\bibitem{kobak2019art}
\begin{barticle}
\bauthor{\bsnm{Kobak}, \binits{D.}},
\bauthor{\bsnm{Berens}, \binits{P.}}:
\batitle{{The art of using t-SNE for single-cell transcriptomics}}.
\bjtitle{Nature Communications}
\bvolume{10}(\bissue{1}),
\bfpage{1}--\blpage{14}
(\byear{2019})
\end{barticle}
\endbibitem

%%% 15
\bibitem{policar2019embedding}
\begin{bchapter}
\bauthor{\bsnm{Poli{\v{c}}ar}, \binits{P.G.}},
\bauthor{\bsnm{Stra{\v{z}}ar}, \binits{M.}},
\bauthor{\bsnm{Zupan}, \binits{B.}}:
\bctitle{{Embedding to reference t-SNE space addresses batch effects in
  single-cell classification}}.
In: \bbtitle{International Conference on Discovery Science},
pp. \bfpage{246}--\blpage{260}
(\byear{2019}).
\bcomment{Springer}
\end{bchapter}
\endbibitem

%%% 16
\bibitem{van2014accelerating}
\begin{barticle}
\bauthor{\bsnm{Van Der~Maaten}, \binits{L.}}:
\batitle{{Accelerating t-SNE using tree-based algorithms}}.
\bjtitle{The Journal of Machine Learning Research}
\bvolume{15}(\bissue{1}),
\bfpage{3221}--\blpage{3245}
(\byear{2014})
\end{barticle}
\endbibitem

%%% 17
\bibitem{kobak2019umap}
\begin{botherref}
\oauthor{\bsnm{Kobak}, \binits{D.}},
\oauthor{\bsnm{Linderman}, \binits{G.C.}}:
{UMAP does not preserve global structure any better than t-SNE when using the
  same initialization}.
bioRxiv
(2019)
\end{botherref}
\endbibitem

%%% 18
\bibitem{kobak2019heavy}
\begin{bchapter}
\bauthor{\bsnm{Kobak}, \binits{D.}},
\bauthor{\bsnm{Linderman}, \binits{G.}},
\bauthor{\bsnm{Steinerberger}, \binits{S.}},
\bauthor{\bsnm{Kluger}, \binits{Y.}},
\bauthor{\bsnm{Berens}, \binits{P.}}:
\bctitle{{Heavy-tailed kernels reveal a finer cluster structure in t-SNE
  visualisations}}.
In: \bbtitle{Joint European Conference on Machine Learning and Knowledge
  Discovery in Databases},
pp. \bfpage{124}--\blpage{139}
(\byear{2019}).
\bcomment{Springer}
\end{bchapter}
\endbibitem

%%% 19
\bibitem{belkina2019automated}
\begin{barticle}
\bauthor{\bsnm{Belkina}, \binits{A.C.}},
\bauthor{\bsnm{Ciccolella}, \binits{C.O.}},
\bauthor{\bsnm{Anno}, \binits{R.}},
\bauthor{\bsnm{Halpert}, \binits{R.}},
\bauthor{\bsnm{Spidlen}, \binits{J.}},
\bauthor{\bsnm{Snyder-Cappione}, \binits{J.E.}}:
\batitle{{Automated optimized parameters for T-distributed stochastic neighbor
  embedding improve visualization and analysis of large datasets}}.
\bjtitle{Nature Communications}
\bvolume{10}(\bissue{1}),
\bfpage{1}--\blpage{12}
(\byear{2019})
\end{barticle}
\endbibitem

%%% 20
\bibitem{sklearn_api}
\begin{bchapter}
\bauthor{\bsnm{Buitinck}, \binits{L.}},
\bauthor{\bsnm{Louppe}, \binits{G.}},
\bauthor{\bsnm{Blondel}, \binits{M.}},
\bauthor{\bsnm{Pedregosa}, \binits{F.}},
\bauthor{\bsnm{Mueller}, \binits{A.}},
\bauthor{\bsnm{Grisel}, \binits{O.}},
\bauthor{\bsnm{Niculae}, \binits{V.}},
\bauthor{\bsnm{Prettenhofer}, \binits{P.}},
\bauthor{\bsnm{Gramfort}, \binits{A.}},
\bauthor{\bsnm{Grobler}, \binits{J.}},
\bauthor{\bsnm{Layton}, \binits{R.}},
\bauthor{\bsnm{VanderPlas}, \binits{J.}},
\bauthor{\bsnm{Joly}, \binits{A.}},
\bauthor{\bsnm{Holt}, \binits{B.}},
\bauthor{\bsnm{Varoquaux}, \binits{G.}}:
\bctitle{{API} design for machine learning software: experiences from the
  scikit-learn project}.
In: \bbtitle{ECML PKDD Workshop: Languages for Data Mining and Machine
  Learning},
pp. \bfpage{108}--\blpage{122}
(\byear{2013})
\end{bchapter}
\endbibitem

%%% 21
\bibitem{jacomy2014forceatlas2}
\begin{barticle}
\bauthor{\bsnm{Jacomy}, \binits{M.}},
\bauthor{\bsnm{Venturini}, \binits{T.}},
\bauthor{\bsnm{Heymann}, \binits{S.}},
\bauthor{\bsnm{Bastian}, \binits{M.}}:
\batitle{{ForceAtlas2, a continuous graph layout algorithm for handy network
  visualization designed for the Gephi software}}.
\bjtitle{PloS One}
\bvolume{9}(\bissue{6}),
\bfpage{98679}
(\byear{2014})
\end{barticle}
\endbibitem

%%% 22
\bibitem{bohm2020unifying}
\begin{botherref}
\oauthor{\bsnm{B{\"o}hm}, \binits{J.N.}},
\oauthor{\bsnm{Berens}, \binits{P.}},
\oauthor{\bsnm{Kobak}, \binits{D.}}:
{A Unifying Perspective on Neighbor Embeddings along the Attraction-Repulsion
  Spectrum}.
arXiv preprint arXiv:2007.08902
(2020)
\end{botherref}
\endbibitem

%%% 23
\bibitem{hochgerner2018conserved}
\begin{barticle}
\bauthor{\bsnm{Hochgerner}, \binits{H.}},
\bauthor{\bsnm{Zeisel}, \binits{A.}},
\bauthor{\bsnm{L{\"o}nnerberg}, \binits{P.}},
\bauthor{\bsnm{Linnarsson}, \binits{S.}}:
\batitle{{Conserved properties of dentate gyrus neurogenesis across postnatal
  development revealed by single-cell RNA sequencing}}.
\bjtitle{Nature Neuroscience}
\bvolume{21}(\bissue{2}),
\bfpage{290}--\blpage{299}
(\byear{2018})
\end{barticle}
\endbibitem

%%% 24
\bibitem{harris2018classes}
\begin{barticle}
\bauthor{\bsnm{Harris}, \binits{K.D.}},
\bauthor{\bsnm{Hochgerner}, \binits{H.}},
\bauthor{\bsnm{Skene}, \binits{N.G.}},
\bauthor{\bsnm{Magno}, \binits{L.}},
\bauthor{\bsnm{Katona}, \binits{L.}},
\bauthor{\bsnm{Gonzales}, \binits{C.B.}},
\bauthor{\bsnm{Somogyi}, \binits{P.}},
\bauthor{\bsnm{Kessaris}, \binits{N.}},
\bauthor{\bsnm{Linnarsson}, \binits{S.}},
\bauthor{\bsnm{Hjerling-Leffler}, \binits{J.}}:
\batitle{{Classes and continua of hippocampal CA1 inhibitory neurons revealed
  by single-cell transcriptomics}}.
\bjtitle{PLoS Biology}
\bvolume{16}(\bissue{6}),
\bfpage{2006387}
(\byear{2018})
\end{barticle}
\endbibitem

%%% 25
\bibitem{Ulyanov2016}
\begin{botherref}
\oauthor{\bsnm{Ulyanov}, \binits{D.}}:
{Multicore-TSNE}.
GitHub
(2016)
\end{botherref}
\endbibitem

%%% 26
\bibitem{pedregosa2011scikit}
\begin{barticle}
\bauthor{\bsnm{Pedregosa}, \binits{F.}},
\bauthor{\bsnm{Varoquaux}, \binits{G.}},
\bauthor{\bsnm{Gramfort}, \binits{A.}},
\bauthor{\bsnm{Michel}, \binits{V.}},
\bauthor{\bsnm{Thirion}, \binits{B.}},
\bauthor{\bsnm{Grisel}, \binits{O.}},
\bauthor{\bsnm{Blondel}, \binits{M.}},
\bauthor{\bsnm{Prettenhofer}, \binits{P.}},
\bauthor{\bsnm{Weiss}, \binits{R.}},
\bauthor{\bsnm{Dubourg}, \binits{V.}}, \betal:
\batitle{{Scikit-learn: Machine learning in Python}}.
\bjtitle{The Journal of Machine Learning Research}
\bvolume{12},
\bfpage{2825}--\blpage{2830}
(\byear{2011})
\end{barticle}
\endbibitem

%%% 27
\bibitem{wong2012points}
\begin{botherref}
\oauthor{\bsnm{Wong}, \binits{B.}}:
Points of view: visualizing biological data
(2012)
\end{botherref}
\endbibitem

%%% 28
\bibitem{jacobs1988increased}
\begin{barticle}
\bauthor{\bsnm{Jacobs}, \binits{R.A.}}:
\batitle{Increased rates of convergence through learning rate adaptation}.
\bjtitle{Neural Networks}
\bvolume{1}(\bissue{4}),
\bfpage{295}--\blpage{307}
(\byear{1988})
\end{barticle}
\endbibitem

\end{thebibliography}
